Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.

### 2014-10-10 Notes/model.tex
Added some notes about numerical integration and actually computing association probability using both hypothesis and reprojection.

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
%\setcounter{page}{4321}
%\DeclareMathSymbol{\Tangent}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\poly}{poly}

@@

Now that we have an association from TP $i$ to point track $j$ through
$\lambda$, we can come up with an association probability
\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{i}_{j,t-1}(\lambda)}
\begin{align}
   \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
\ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
&=(\max \{ 0, \nabla \occf^\top \ray \})^2
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
\end{align}

Now coming back to our point track energy, the distribution over $\lambda$
becomes our association function which instead of associating each point track
with a traffic participant, associates it with a depth ($\lambda$). Hence our
summation over $N$ traffic participants is replaced by an integral over the
entire ray.
\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i,\{ \dimsn{i} \}_i) = \\
    \sum_{i = 1}^N
    \sum_{j = 1}^{M}
    \int_1^{\infty}
    a^i_{j,t-1}(\lambda) 
    \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
    d\lambda
\end{multline}

@@

\begin{multline}
  \label{eq:integrand}
  \Energy{track}(.) = 
    \sum_{i = 1}^N
    \sum_{j = 1}^{M}
    \int_1^{\infty}
    \assocP
    E^i_{\text{reproj}}(\lambda)
    d\lambda
\end{multline}
where $x = \lambda \ray$ and $E^i_{\text{reproj}}(\lambda) = \|\trackpj{t} -
f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
quadratic in $\lambda$

@@

>>>>

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
%\setcounter{page}{4321}
%\DeclareMathSymbol{\Tangent}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\poly}{poly}
\DeclareMathOperator*{\argmin}{\arg\min}

@@

Now that we have an association from TP $i$ to point track $j$ through
$\lambda$, we can come up with an association probability
\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{i}_{j,t-1}(\lambda)}
\newcommand{\assocPk}{a^{i}_{j,t-1}(\lambda_k)}
\begin{align}
   \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
\ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
&=(\max \{ 0, \nabla \occf^\top \ray \})^2
  \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
\end{align}

Note that this fraction although called association probability does not
capture the entire information that we have available for compute association
of points to tracks. This above fraction is the association probability given 
the hypothesized parameters of traffic participant model. Given that a point is
observed on the image the sum of probability marginalized over other parameters
must be one i.e.
\begin{align}
    \sum_{i = 1}^N
    \int_1^{\infty}
    \assocP d\lambda = 1
\end{align}

To compute the association probability between traffic participant $i$ and
point track $j$ we must use re-projection error as well. When the association
$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
re-projection error must be zero, otherwise the error becomes a measure of
distance from the true solution:

\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
\begin{align}
  \Ereproj(\lambda) = \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
\end{align}

The error terms can be converted to probability domain by considering the error
term as negative log of probablity

\begin{align}
  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))
\end{align}

Using both the evidence terms we can write probability of association as
\begin{align}
  P^{(ij)}_{\text{assoc}} \propto \int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
  \label{eq:prob-assoc}
\end{align}

However, for estimating the overall energy we just need to compute the expected
value of the re-projection error for given parameters, i.e.

\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i,\{ \dimsn{i} \}_i) = \\
    \sum_{i = 1}^N
    \sum_{j = 1}^{M}
    \int_1^{\infty}
    a^i_{j,t-1}(\lambda) 
    \|\trackpj{t} - f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2
    d\lambda
\end{multline}

If the aim is to find the best possible association, it is easier as we need to
to compute the association that minimizes the expected re-projection error for
point $j$. It remains to be seen that how the minima of following expression relates to minima of \eqref{eq:prob-assoc}

\begin{align}
  i^* = \argmin_{i=1}^N \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
\end{align}

Since the computation of $\assocP$ entirely depends on hypothesized parameters,
it severely limits the applicability of this method outside this kind of
parameterized model.

@@

\begin{multline}
  \label{eq:integrand}
  \Energy{track}(.) = 
    \sum_{i = 1}^N
    \sum_{j = 1}^{M}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
\end{multline}
where $x = \lambda \ray$ and $\Ereproj(\lambda) = \|\trackpj{t} -
f^i_{reproj}(\trackpj{t-1}, \lambda)\|^2$ is reprojection error which is a
quadratic in $\lambda$

@@

\subsection{Numerical integration}
Numerical integration is possible by computed by sampling. Samples need to be
generated from the association probability $\assocP$ for a given $j$. We take
proposal distribution to be a GMM with modes around probable reflection points.
The weights of all Gaussians in the mixture are proportional to the distance of
the point $j$ from projection of ellipsoid centre i.e. $\|\trackpj{t} - \projectionOf{\relp{i}{t}}\|$ . The range of Gaussian $G_i$
must be in the interval $[\|\relp{i}{t}\|, \|\relp{i}{t}\| +
\sqrt{3}\max(\dimsn{i})]$. Hence we take the mean as $\|\relp{i}{t}\| +
\frac{\sqrt{3}}{2}\max(\dimsn{i})$ and variance as
$\frac{1}{3}\max(\dimsn{i})^2$. The distribution from which we sample is 
\newcommand{\Gauss}{\mathcal{N}}
\newcommand{\PropDist}{\mathcal{W}}
\begin{align}
  \PropDist(\lambda) = \sum_i A_i \Gauss(\lambda; \|\relp{i}{t}\| +
  \frac{\sqrt{3}}{2}\max(\dimsn{i}), \frac{1}{\sqrt{3}}\max(\dimsn{i}))
\end{align}
And the numerical integral with $K$ samples is computed by
\begin{align}
    \int_1^{\infty}
    \assocP
    \Ereproj(\lambda)
    d\lambda
    =
    \frac{1}{K}\sum_k \Ereproj \frac{\assocPk}{\PropDist(\lambda_k)}
\end{align}
where $\lambda_k$ is the $k$th sample drawn from $\PropDist(\lambda)$.
